---
title: "p8105_hw5_sd3731"
author: "Susie Dong"
date: "2023-11-13"
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1

Describe the raw data.
```{r , message=FALSE}
homicide = read_csv("./data/homicide-data.csv")
```

**Variables**:

- `uid`: unique identifier

- `reported_date`: date of homicide accident

- `victim_last`: last name of victim

- `victim_first`: first name of victim

- `victim_race`: race name of victim

- `victim_age`: age name of victim

- `victim_sex`: sex name of victim

- `city`: city location of homicide accident

- `state`: state location of homicide accident

- `lat`: latitude location of homicide accident

- `lon`: longitude location of homicide accident

- `disposition`: disposition outcome of homicide accident

The dataset `homicide` contains information about homicide cases in United States from 2007 to 2017. It contains `r nrow(homicide)` rows and `r ncol(homicide)` variable, where each row is a criminal homicide case. The dataset includes the time the case was reported, the information about victims, the location of killing, and whether an arrest was made. 

```{r}
homicide =
  mutate(
    city_state = str_c(city, ", ", state)
  )
```

```{r}
homicide |> 
  count(city_state)

homicide |> 
  filter(str_detect(disposition, "Open|without")) |> 
  count(city_state)

homicide_Baltimore <-
  homicide |> 
  filter(city_state == "Baltimore, MD")|> 
  count(disposition)

prop_res <- 
  prop.test(x = homicide_Baltimore$n[[2]] + homicide_Baltimore$n[[3]], 
          n = sum(homicide_Baltimore$n), 
          p = 0.5) |> 
  broom::tidy()

prop_res |> 
  pull(estimate, conf.low)
```

## R Markdown


